---
title: "Data Analysis"
output: html_notebook
---
## Libraries
```{r}
library(dplyr)
library(ggplot2)
```

## Read and prepare data
```{r}
# If you want to run our file, you only have to change this path to the correct path on your local machine.
d <- read.csv("/Users/moutpessemier/Desktop/MT/A-Survey-On-The-Impact-of-Customer-Chatbots-on-E-commerce/DataAnalysis/data.csv", sep=",")
```

The data has been anonimised in Excel. A new column was created called 'taskCategory'. The tasks performed are categorised in one of the following 4 categories:

- FAQ
- Personalised question
- Complaint
- Sales

From the 48 entries, we had to throw 3 away:

- 2 because of the used chatbot: they were no telecom chatbots.
- 1 entry was a duplicate.

Some of the columns were renamed to have an easier time working with the variable names
```{r}
names(d)[names(d) == "How.old.are.you."] <- "age"
names(d)[names(d) == "What.is.the.highest.degree.you.currently.have."] <- "degree"
names(d)[names(d) == "What.is.your.gender."] <- "gender"
names(d)[names(d) == "Which.company.s.chatbot.did.you.interact.with."] <- "chatbot"
names(d)[names(d) == "In.what.language.did.you.interact.with.the.chatbot."] <- "language"
names(d)[names(d) == "Through.which.platform.did.you.interact.with.the.chatbot."] <- "platform"

# Comparative study questions
names(d)[names(d) == "Did.you.have.any.difficulties.using.the.chatbot."] <- "q1"
names(d)[names(d) == "The.chatbot.did.not.ask.the.right.questions.to.solve.your.task."] <- "q2"
names(d)[names(d) == "The.chatbot.didn.t.know.what.he.was.talking.about."] <- "q3"
names(d)[names(d) == "Was.the.chatbot.polite."] <- "q4"
names(d)[names(d) == "Did.the.chatbot.fulfil.your.task.correctly."] <- "q5"
names(d)[names(d) == "Was.the.chatbot.easy.to.use."] <- "q6"
names(d)[names(d) == "Was.it.a.task.to.interact.with.the.chatbot."] <- "q7"
names(d)[names(d) == "Did.the.chatbot.need.help.from.a.help.desk.agent.to.complete.your.task."] <- "q8"
names(d)[names(d) == "Did.the.chatbot.contain.enough.knowledge.to.help.with.your.problem."] <- "q9"
names(d)[names(d) == "Did.you.enjoy.interacting.with.the.chatbot."] <- "q10"
names(d)[names(d) == "Was.the.chatbot.capable.of.completing.the.task.on.its.own."] <- "q11"
names(d)[names(d) == "Did.the.chatbot.ask.you.relevant.questions.to.gather.the.information.to.solve.your.task."] <- "q12"
names(d)[names(d) == "Did.the.chatbot.deliver.a.better.quality.of.service.than.a.human."] <- "q13"
names(d)[names(d) == "Did.the.chatbot.interact.in.a.respectful.way."] <- "q14"
names(d)[names(d) == "Was.the.chatbot.unable.to.complete.your.task."] <- "q15"
names(d)[names(d) == "The.service.provided.by.the.human.was.of.better.quality."] <- "q16"
names(d)[names(d) == "Did.you.feel.you.could.trust.the.information.provided.by.the.chatbot."] <- "q17"
names(d)[names(d) == "Did.the.chatbot.perform.the.task.as.you.expected.it.to."] <- "q18"
names(d)[names(d) == "Could.you.solve.your.problem.question.after.using.the.chatbot."] <- "q19"

# Importance Study questions
# Scenario 1
names(d)[names(d) == "The.chatbot.DOES.NOT.execute.the.given.task.successfully."] <- "s1q1"
names(d)[names(d) == "The.chatbot.can.NOT.perform.the.requested.service.to.the.same.level.as.a.human.agent."] <- "s1q2"
names(d)[names(d) == "The.chatbot.knows.at.least.as.much.as.an.agent.about.the.requested.service."] <- "s1q3"
names(d)[names(d) == "The.chatbot.executes.the.given.task.successfully."] <- "s1q4"
names(d)[names(d) == "The.chatbot.knows.less.than.an.agent.about.the.requested.service."] <- "s1q5"
names(d)[names(d) == "The.chatbot.can.perform.the.requested.service.to.the.same.level.as.a.human.agent."] <- "s1q6"

# Scenario 2
names(d)[names(d) == "The.chatbot.DOES.NOT.execute.the.given.task.successfully..1"] <- "s2q1"
names(d)[names(d) == "The.chatbot.can.NOT.perform.the.requested.service.to.the.same.level.as.a.human.agent..1"] <- "s2q2"
names(d)[names(d) == "The.chatbot.knows.at.least.as.much.as.an.agent.about.the.requested.service..1"] <- "s2q3"
names(d)[names(d) == "The.chatbot.executes.the.given.task.successfully..1"] <- "s2q4"
names(d)[names(d) == "The.chatbot.knows.less.than.an.agent.about.the.requested.service..1"] <- "s2q5"
names(d)[names(d) == "The.chatbot.can.perform.the.requested.service.to.the.same.level.as.a.human.agent..1"] <- "s2q6"

# Scenario 3
names(d)[names(d) == "The.chatbot.DOES.NOT.execute.the.given.task.successfully..2"] <- "s3q1"
names(d)[names(d) == "The.chatbot.can.NOT.perform.the.requested.service.to.the.same.level.as.a.human.agent..2"] <- "s3q2"
names(d)[names(d) == "The.chatbot.knows.at.least.as.much.as.an.agent.about.the.requested.service..2"] <- "s3q3"
names(d)[names(d) == "The.chatbot.executes.the.given.task.successfully..2"] <- "s3q4"
names(d)[names(d) == "The.chatbot.knows.less.than.an.agent.about.the.requested.service..2"] <- "s3q5"
names(d)[names(d) == "The.chatbot.can.perform.the.requested.service.to.the.same.level.as.a.human.agent..2"] <- "s3q6"

# General
names(d)[names(d) == "The.chatbot.is.NOT.available.at.all.times."] <- "gq1"
names(d)[names(d) == "The.chatbot.is.easy.to.use."] <- "gq2"
names(d)[names(d) == "The.chatbot.communicates.in.a.robotic...non.empathic.way."] <- "gq3"
names(d)[names(d) == "The.chatbot.is.available.at.all.times."] <- "gq4"
names(d)[names(d) == "The.chatbot.is.NOT.easy.to.use."] <- "gq5"
names(d)[names(d) == "At.times.I.didnt.understand.what.the.chatbot.expected.of.me."] <- "gq6"
```

Now we sort per chatbot provider:
```{r}
telenet <- filter(d, chatbot == "Telenet")
proximus <- filter(d, chatbot == "Proximus")
orange <- filter(d, chatbot == "Orange")
tMobile <- filter(d, chatbot == "T-Mobile")
KPN <- filter(d, chatbot == "KPN")
```

## Data Exploration
### Telenet
```{r}
meanAgeTelenet = mean(telenet$age)
meanAgeTelenet
varAgeTelenet = sd(telenet$age)
varAgeTelenet

barplot(table(telenet$taskCategory),
        main="Frequency of each category in Telenet",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(telenet$language),
        main="Frequency of each language interaction in Telenet",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(telenet$platform),
        main="Frequency of each platform in Telenet",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(telenet$gender),
        main="Frequency of each gender in Telenet",
        xlab="Task Category",
        ylab="Count",
        col=c("red", "blue"))

barplot(table(telenet$degree),
        main="Frequency of each degree in Telenet",
        xlab="Task Category",
        ylab="Count",
        cex.names=0.55,
        col="blue")
```

### Proximus
```{r}
meanAgeProximus = mean(proximus$age)
meanAgeProximus
varAgeProximus = sd(proximus$age)
varAgeProximus

barplot(table(proximus$taskCategory),
        main="Frequency of each category in Proximus",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(proximus$language),
        main="Frequency of each language interaction in Proximus",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(proximus$platform),
        main="Frequency of each platform in Proximus",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(proximus$gender),
        main="Frequency of each gender in Proximus",
        xlab="Task Category",
        ylab="Count",
        col=c("red", "blue"))

barplot(table(proximus$degree),
        main="Frequency of each degree in Proximus",
        xlab="Task Category",
        ylab="Count",
        cex.names=0.55,
        col="blue")
```

### T-Mobile
```{r}
meanAgeTmobile = mean(tMobile$age)
meanAgeTmobile
varAgeTmobile = sd(tMobile$age)
varAgeTmobile

barplot(table(tMobile$taskCategory),
        main="Frequency of each category in T-Mobile",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(tMobile$language),
        main="Frequency of each language interaction in T-Mobile",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(tMobile$platform),
        main="Frequency of each platform in T-Mobile",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(tMobile$gender),
        main="Frequency of each gender in T-Mobile",
        xlab="Task Category",
        ylab="Count",
        col=c("blue"))

barplot(table(tMobile$degree),
        main="Frequency of each degree in T-Mobile",
        xlab="Task Category",
        ylab="Count",
        cex.names=0.55,
        col="blue")
```

### Orange
```{r}
meanAgeOrange = mean(orange$age)
meanAgeOrange
varAgeOrange = sd(orange$age)
varAgeOrange

barplot(table(orange$taskCategory),
        main="Frequency of each category in Orange",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(orange$language),
        main="Frequency of each language interaction in Orange",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(orange$platform),
        main="Frequency of each platform in Orange",
        xlab="Task Category",
        ylab="Count",
        col="blue")

barplot(table(orange$gender),
        main="Frequency of each gender in Orange",
        xlab="Task Category",
        ylab="Count",
        col=c("blue"))

barplot(table(orange$degree),
        main="Frequency of each degree in Orange",
        xlab="Task Category",
        ylab="Count",
        cex.names=0.55,
        col="blue")
```

### KPN
```{r}
#meanAgeKPN = mean(KPN$age)
#meanAgeKPN
#varAgeKPN = sd(KPN$age)
#varAgeKPN

#barplot(table(KPN$taskCategory),
        #main="Frequency of each category in KPN",
        #xlab="Task Category",
        #ylab="Count",
        #col="blue")

#barplot(table(KPN$language),
        #main="Frequency of each language interaction in KPN",
        #xlab="Task Category",
        #ylab="Count",
        #col="blue")

#barplot(table(KPN$platform),
        #main="Frequency of each platform in KPN",
        #xlab="Task Category",
        #ylab="Count",
        #col="blue")

#barplot(table(KPN$gender),
        #main="Frequency of each gender in KPN",
        #xlab="Task Category",
        #ylab="Count",
        #col=c("red", "blue"))

#barplot(table(KPN$degree),
        #main="Frequency of each degree in KPN",
        #xlab="Task Category",
        #ylab="Count",
        #cex.names=0.55,
        #col="blue")
```

### Environment variables
#### Age
```{r}
ggplot(d, aes(x=chatbot, y=age)) + geom_point(colour="black", size=1) + stat_summary(fun=mean, geom="point", shape=1, size=2, colour="red", fill="red") + ggtitle("Age per chatbot provider")
```

#### Degree
```{r}
dfDegree <- d %>%
  group_by(degree) %>%
  count() %>%
  ungroup() %>%
  mutate(perc = `n` / sum(`n`)) %>%
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

ggplot(dfDegree, aes(x="",y=perc, fill=degree)) + geom_col() + coord_polar(theta="y") + geom_text(aes(label = labels), position = position_stack(vjust = 0.5))
```

#### Gender
```{r}
dfGender <- d %>%
  group_by(gender) %>%
  count() %>%
  ungroup() %>%
  mutate(perc = `n` / sum(`n`)) %>%
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

ggplot(dfGender, aes(x="",y=perc, fill=gender)) + geom_col() + coord_polar(theta="y") + geom_text(aes(label = labels), position = position_stack(vjust = 0.5))
```

#### Chatbot
```{r}
dfChatbot <- d %>%
  group_by(chatbot) %>%
  count() %>%
  ungroup() %>%
  mutate(perc = `n` / sum(`n`)) %>%
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

ggplot(dfChatbot, aes(x="",y=perc, fill=chatbot)) + geom_col() + coord_polar(theta="y") + geom_text(aes(label = labels), position = position_stack(vjust = 0.5))
```

#### Language
```{r}
dfLang <- d %>%
  group_by(language) %>%
  count() %>%
  ungroup() %>%
  mutate(perc = `n` / sum(`n`)) %>%
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

ggplot(dfLang, aes(x="",y=perc, fill=language)) + geom_col() + coord_polar(theta="y") + geom_text(aes(label = labels), position = position_stack(vjust = 0.5))
```

#### Platform
```{r}
dfPlat <- d %>%
  group_by(platform) %>%
  count() %>%
  ungroup() %>%
  mutate(perc = `n` / sum(`n`)) %>%
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

ggplot(dfPlat, aes(x="",y=perc, fill=platform)) + geom_col() + coord_polar(theta="y") + geom_text(aes(label = labels), position = position_stack(vjust = 0.5))
```
## Comparative Study
<!-- shift focus to from company based to task category based -->

## Importance Study

